Supplementary Material for: A Rough Guide to Pre-processing High-Frequency Animal Tracking Data

### 2021-02-11 06_bat_data.Rmd
package lib arrange

```{r}
# load libs
library(data.table)
library(RSQLite)
library(ggplot2)
library(patchwork)

# atlastools
library(atlastools)

@@

```{r}
# load recurse
library(recurse)

# split the data
data_smooth <- split(data_smooth, data_smooth$TAG)
```

>>>>

```{r}
# libs for data
library(data.table)
library(RSQLite)
library(atlastools)

# libs for plotting
library(ggplot2)
library(patchwork)

# recursion analysis
library(recurse)

@@

```{r}
# split the data
data_smooth <- split(data_smooth, data_smooth$TAG)
```
